### 2024-03-06 sections/3algebras.tex
Added gluing example.

\subsection{Factorization Algebras on Intervals}\label{ssec:lcfa_on_1d_man}

@@

\begin{corollary}
    There is an equivalence between the $\infty$-categories of locally constant factorization algebras on the closed interval and algebras over the $\infty$-operad $\mathsf{Assoc^{RL}}$
    %
    \begin{equation}
        \lcfa_{[-1,1]} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathsf{Assoc^{RL}}} (\catC).
    \end{equation} 
\end{corollary}

>>>>

\subsection{Factorization Algebras on Intervals}\label{ssec:lcfa_on_ints}

@@

\begin{corollary}\label{cor:lcfas_on_closed_int}
    There is an equivalence between the $\infty$-categories of locally constant factorization algebras on the closed interval and algebras over the $\infty$-operad $\mathsf{Assoc^{RL}}$
    %
    \begin{equation}
        \lcfa_{[-1,1]} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathsf{Assoc^{RL}}} (\catC).
    \end{equation} 
\end{corollary}

### 2024-03-06 sections/4gluing.tex
Added gluing example.

\begin{lemma}\label{lem:fbar_func}
    A collar-gluing $f:M \xrightarrow{} [-1,1]$ of a stratified manifold $M$ induces a functor
    %
    \begin{equation}
        \bar{f}: \mfld_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld_{/M}),
    \end{equation}
    %
    which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$. Moreover, this functor is even an algebra.
\end{lemma}

@@

    Sticking to $\mfld[r]_{/M}$ though, the assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
    %
    \begin{equation}
        \begin{tikzcd}
            N_0 \times \mathbb{R} \arrow[r, hook, "e_0"] \arrow[d, hook] & N'_0 \times \mathbb{R} \arrow[d, hook]\\
            N_- \arrow[r, hook, "e_-"] & N'_-,
            \end{tikzcd}
    \end{equation}
    %
    so that we clearly get a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}).
    \end{equation}

    Need to be extended to $\mfld_{/M}$ by dealing with the homotopies.

    %Formally, the relevant definition is \cite[def.2.1.2.7]{lurie_ha}, which says that we have to check two things: that the constructed functor $\gamma(A_-, A_+)$ lies over $\mathsf{Fin}_*$ and that it sends inert morphisms to inert morphisms. Factorization homology, $\int_- A_{0,\pm}$, satisfies this almost by definition, while \cref{lem:B_sym_mon} tells us that the bar construction similarly does so. All that is left to show is that $\bar{f}$ is a map of $\infty$-operads. But this is obviously the case since all it is doing is splitting the input into pieces while keeping track of how they relate to each other.
\end{proof}

@@

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.

    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences.
\end{example}

>>>>

\begin{lemma}\label{lem:fbar_func}
    A collar-gluing $f:M \xrightarrow{} [-1,1]$ of a stratified manifold $M$ induces a functor
    %
    \begin{equation}
        \bar{f}: \mfld_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld_{/M}),
    \end{equation}
    %
    which on objects acts as $(N \xhookrightarrow{} M) \mapsto (N_- \xhookrightarrow{} M, N_0 \times \mathbb{R} \xhookrightarrow{} M, N_+ \xhookrightarrow{} M)$. Moreover, this functor is even a map of $\infty$-operads.
\end{lemma}

@@

    Sticking to $\mfld[r]_{/M}$ though, the assignment clearly plays well with the algebra structure of the right-hand side, through the existence of (on the nose) commutative diagrams like e.g.
    %
    \begin{equation}
        \begin{tikzcd}
            N_0 \times \mathbb{R} \arrow[r, hook, "e_0"] \arrow[d, hook] & N'_0 \times \mathbb{R} \arrow[d, hook]\\
            N_- \arrow[r, hook, "e_-"] & N'_-,
            \end{tikzcd}
    \end{equation}
    %
    so that we clearly get a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}).
    \end{equation}
    %
    That the functor is a map of $\infty$-operads is clear from the fact that the key role on both sides is played by disjoint union.

    {\color{red}Needs to be extended to $\mfld_{/M}$ by dealing with the homotopies. Alternatively, we can prove the theorem for $\disk[r]_{/M}$-algebras first and then argue at the factorization algebra level that the glued algebra has to inherit local constancy.}
\end{proof}

@@

\begin{example}\label{ex:reproduce_lcfas_on_interval}
    With the ingredients we have introduced up to now, specifically in \cref{ssec:lcfa_on_ints}, we can do a nontrivial check of the gluing theorem. This is because we can write a collar-gluing of the closed interval $[-1,1] \cong \left[-1,1\right) \coprod_{(-1,1)} \left(-1,1\right] \cong \mathbb{R}_{\geq 0} \coprod_{\mathbb{R}} \mathbb{R}_{\leq 0}$. We note here that we have written $\mathbb{R}_{\leq 0}$ and $\mathbb{R}_{\geq 0}$ to emphasize the maps forming the decomposition. At the level of unstructured objects these two are isomorphic (see also \cref{rem:left_or_right_module}). For this example, the theorem says that locally constant factorization algebras on the closed interval should be given by
    %
    \begin{equation}
        \lcfa_{[-1,1]} (\catC) \simeq \lcfa_{\mathbb{R}_{\geq 0}} (\catC) \bigtimes_{\lcfa_{\mathbb{R}} (\catC)} \lcfa_{\mathbb{R}_{\leq 0}} (\catC) \simeq \mathsf{RMod} (\catC) \bigtimes_{\alg{\mathbb{E}_1} (\catC)} \mathsf{LMod} (\catC),
    \end{equation}
    %
    where the functors are the ones that forget the module. At the level of objects, this is the data of an algebra with a right module $(A, R) \in \mathsf{RMod} (\catC)$ and an algebra with a left module $(B, L) \in \mathsf{LMod} (\catC)$, such that the algebras are equal $A = B$. But this is exactly the same as the description we gave in terms of an algebra with a left and a right module, i.e. an algebra over $\mathsf{Assoc^{RL}}$, in \cref{cor:lcfas_on_closed_int}.
\end{example}

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    A highly nontrivial check of the gluing theorem is given by the circle $S^1$. Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. This result is not generalizable to higher spheres because it uses the technology of covering spaces. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Unlike the covering space result for the circle \cite[sec.5.5]{ginot2015} which doesn't generalize to higher spheres, the gluing theorem has no such restriction. Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.

    From this example we can easily see that beyond the dimensionality $n$ of the space, which is locally kept track of as an $\mathbb{E}_n$-algebra, locally constant factorization algebras for the higher spheres also keep track of higher coherent (self-)equivalences, which imitate traingulations of the spheres.
\end{example}

### 2024-03-06 sections/5classification.tex
Added gluing example.

In \cref{ssec:lcfa_on_Rn} we discussed locally constant factorization algebras on Euclidean spaces of different dimension $n$, and we saw that they presented the data of $\mathbb{E}_n$-algebras. In \cref{ssec:lcfa_on_1d_man}, on the other hand we focused on 1 dimensional manifolds, but with different possible stratification structures, and we saw that the data encoded in defects was a module structure. Here, in the spirit of this section, we work to extend both of these developments to the case of Euclidean spaces with the specific kind of defect that we have limited ourselves to, namely, $\mathbb{R}^{d \subset n}$.

>>>>

In \cref{ssec:lcfa_on_Rn} we discussed locally constant factorization algebras on Euclidean spaces of different dimension $n$, and we saw that they presented the data of $\mathbb{E}_n$-algebras. In \cref{ssec:lcfa_on_ints}, on the other hand we focused on 1 dimensional manifolds, but with different possible stratification structures, and we saw that the data encoded in defects was a module structure. Here, in the spirit of this section, we work to extend both of these developments to the case of Euclidean spaces with the specific kind of defect that we have limited ourselves to, namely, $\mathbb{R}^{d \subset n}$.
